<i>invivoPKfit</i> and <i>CvTdb</i> figures

### 2022-10-27 MainAnalysis.Rmd
Trying to add DTXSIDs

# data <- read.csv("inst/ext/cvt_query_for_john_27may2021_v2.csv")
# data <- read.csv("inst/ext/cvtdb_invivopkfit_02242022.csv")
# data <- read.csv("inst/ext/cvtdb_invivopkfit_04142022.csv")
cvt.data <- read.csv("inst/ext/cvtdb_invivopkfit_04262022.csv")

@@

```{r, run_invivoPKfit_1comp, eval = TRUE}
THIS.DATE <- "102422"
### do 1-Compartment fit
system.time(PK.fit.table.1comp <- fit_all(
  data.set = cvt.data,
  model = "1compartment",
  modelfun = "analytic",
  compound.col = "analyte_name_original",
  cas.col = "dsstox_casrn",
  reference.col = "fk_reference_document_id",
  species.col = "species",
  species.weight.col = "weight_kg",
  species.weight.units.default = "kg",
  dose.col = "dose_level_normalized",
  time.col = "time_hr",
  time.units.default = "hr",
  media.col = "conc_medium_normalized",
  media.units.default = "normalized",
  value.col = "conc",
  units.default = NA,
  route.col = "administration_route_normalized",
  source.col = "document_id",
  loq.default = NA,
  subject.default = NA,
  info.default = NA
))
```

```{r, plot_1comp, eval=FALSE}
plot_conctime(PK.fit.table.1comp[[1]],cvt.data,"1compartment")
head(subset(PK.fit.table.1comp[[1]],Vdist>10000&!is.infinite(AIC)&param.value.type=="Fitted geometric mean"))
```

@@

>>>>

# data <- read.csv("inst/ext/cvt_query_for_john_27may2021_v2.csv")
# data <- read.csv("inst/ext/cvtdb_invivopkfit_02242022.csv")
# data <- read.csv("inst/ext/cvtdb_invivopkfit_04142022.csv")
cvt.data <- read.csv("inst/ext/cvtdb_invivopkfit_04262022-2.csv")

@@

```{r, set_file_timestamp, eval = TRUE}
THIS.DATE <- "102422"
```

```{r, run_invivoPKfit_1comp, eval = FALSE}
### do 1-Compartment fit
system.time(PK.fit.table.1comp <- fit_all(
  data.set = cvt.data,
  model = "1compartment",
  modelfun = "analytic",
  compound.col = "analyte_name_original",
  dtxsid.col = "dsstox_substance_id",
  cas.col = "dsstox_casrn",
  reference.col = "fk_reference_document_id",
  species.col = "species",
  species.weight.col = "weight_kg",
  species.weight.units.default = "kg",
  dose.col = "dose_level_normalized",
  time.col = "time_hr",
  time.units.default = "hr",
  media.col = "conc_medium_normalized",
  media.units.default = "normalized",
  value.col = "conc",
  units.default = NA,
  route.col = "administration_route_normalized",
  source.col = "document_id",
  loq.default = NA,
  subject.default = NA,
  info.default = NA
))
```

@@

```{r, merge_pkfits, eval=FALSE}
all.fit.table <- merge_model_fits(list("1compartment"=pk_output_1comp,
                                       "2compartment="=pk_output_2comp,
                                       "flat"=pk_output_flat))
